---
title: "Bankruptcy 2"
author: "Team Finance"
date: "July 1, 2023"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
    code_folding: hide
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# Correlation Function

```{r}

corfunction=function(d){
  mycorr=cor(d[, 1:ncol(d)]); p.mat=ggcorrplot::cor_pmat(d[,1:ncol(d)])
  myplot=ggcorrplot(mycorr, hc.order=TRUE,type="lower",
                    colors=c("red", "white","green"),tl.cex = 8, 
                    tl.col = "black", lab=TRUE, lab_size=2, p.mat=p.mat,
                    insig="pch", pch=4)
  print(myplot)}

```



# Load Libraries 

```{r}
######################
require(Amelia)      #  
require(dplyr)       #
require(e1071)       #
require(kableExtra)  #
require(magrittr)    #
require(tidyverse)   #
require(fpp3)        #
require(glmm)        #  
require(MASS)        #
require(car)         #
require(elsa)        #
require(fastDummies) #
require(ggplot2)     #
require(ggcorrplot)  #
require(ggExtra)     #
require(glmmML)      #
require(grid)        #
require(gridExtra)   #
require(kableExtra)  #
require(imbalance)   #
library(leaflet)     #
library(leaflet.extras)
require(psych)       #
require(raster)      #
require(RColorBrewer)#
require(rgdal)       #
require(rgeos)       #
require(shiny)       #
require(sf)          #
require(sp)          #
require(spatialreg)  #
require(spData)      #
require(spdep)       #
require(tmap)        #
require(tmaptools)   #
require(spdep)       #
require(tidyverse)   #
require(leaps)       #
require(caret)       #
require(glmnet)      #
require(lmSupport)   #
require(lars)        #
require(glmpath)     #
require(covTest)     #
gc()
```
# Printing / Citation Functions

```{r}

myprint=function(x){x%>%kbl()%>%kable_classic(html_font = "Cambria")}
mycite=function(x){citation(x)}

```


# Set Directory / Load Data / EDA

```{r}

myprint=function(x){x%>%kbl()%>%kable_classic(html_font = "Cambria")}
mycite=function(x){citation(x)}
setwd('C:/Users/lfult/Documents/Bankruptcy Study/')
bankrupt=read.csv('bankruptcy_again.csv', stringsAsFactors = T)
missmap(bankrupt, x.cex=.5)

```

## Missing by Column

```{r}

myc = function(x){
  co=rep(0,ncol(bankrupt))
  for (i in 1:ncol(x)){co[i]=sum(is.na(x[1:nrow(x), i]))}
  names(co)=colnames(bankrupt)
  co=sort(co, decreasing=T)/nrow(bankrupt)
  print(length(co[co>.2]))
  tmp=co[1:13]
  barplot(tmp, las=2, cex.names=.5, space=0)
  print(names(tmp))
  return(co)
}

myc(bankrupt)

```

## Missing by Row

```{r}

myr = function (x){
  temp=rep(0,nrow(x))
  for (i in 1:nrow(x)){
    temp[i]=
    sum(is.na(x[i, 1:ncol(x)]))/ncol(x)}
  x$ROWMISS=temp
  x=x[order(-x$ROWMISS), ]
  return(x)
}

bankrupt=myr(bankrupt)
tmp=bankrupt$ROWMISS[1:20]
names(tmp)=bankrupt$HOSPITAL_NAME[1:20]
tmp
  
```

## Deleted Unreliable Observations that were not bankrupt

Villa Feliciano
Hospital Universitario Dr Ruiz Arnau 
Florida State Hospital
San Juan City Hospital
Patients Choice Medical Center of Smith County in 2012
Ascension St Mary Kankakee (FKA AMITA Health St Marys Hospital Kankakee)
MISH Hospital and Clinics (AKA Institute for Advanced Bariatric Surgery) 
Ochsner Medical Center - Kenner 
Rockefeller University Hospital 
University District Hospital 
Lindsay Municipal Hospital 
Hawkins County Memorial Hospital (FKA Wellmont Hawkins County Memorial Hospital) 
TrustPoint Hospital 
McLeod Behavioral Health Darlington (FKA Wilson Hospital) 
Texas Center for Infectious Disease (FKA San Antonio State Chest Hospital) 
Fayette Medical Center (FKA Weimer Medical Center) 
Apire Hospital (FKA Aspire Behavioral Health of Conroe) 
Lonesome Pine
Jefferson Hospital
Massachusetts Eye and Ear
Hackettstown Medical Center
Hospital Oncologico Andres Grillasca


## Impute Missing

```{r}

for(i in 1:ncol(bankrupt)){
  if(is.numeric(bankrupt[,i])){
    bankrupt[is.na(bankrupt[,i]), i] <- median(bankrupt[,i], na.rm = TRUE)
  }
}

```


## Proxies for Altman and Ohlson

```{r}

#Owners' equity, argued by Brad...calculate changes for hospital t-(t-1) for the change in equity
TA=ifelse(bankrupt$TotalAssets>0,bankrupt$TotalAssets,.01)
TL=ifelse(bankrupt$TotLiab>0, bankrupt$TotLiab,.01)
CA=ifelse(bankrupt$CurrentAssets==0, .01, bankrupt$CurrentAssets)
bankrupt$AltmanX1=(bankrupt$CurrentAssets-bankrupt$CurLiab)/TA#Altman X1 
bankrupt$AltmanX2=bankrupt$EquityProxy/TA
bankrupt$AltmanX3=bankrupt$EBITDA/TA
bankrupt$AltmanX4=bankrupt$EquityProxy/TL
bankrupt$AltmanZ=6.56*bankrupt$AltmanX1+3.26*bankrupt$AltmanX2+6.72*bankrupt$AltmanX3+1.05*bankrupt$AltmanX4

bankrupt$OhlsonX1=log(TA/696)
bankrupt$OhlsonX2=bankrupt$TotLiab/TA
bankrupt$OhlsonX3=(bankrupt$CurrentAssets-bankrupt$CurLiab)/TA
bankrupt$OhlsonX4=(bankrupt$CurLiab/CA)
bankrupt$OhlsonX5=ifelse(bankrupt$TotLiab>bankrupt$TotalAssets,1,0)
bankrupt$OhlsonX6=bankrupt$NetIncome/TA
bankrupt$OhlsonX7=bankrupt$EBITDA/TL
bankrupt$OhlsonX8=bankrupt$Loss2Years
bankrupt$OhlsonX9=bankrupt$NetDelta

#bankrupt$AltmanZ=6.56*bankrupt$AltmanX1+3.26*bankrupt$AltmanX2+6.72*bankrupt$AltmanX3+1.05*bankrupt$AltmanX4
#bankrupt$OhlsonO=-1.32-0.407*bankrupt$OhlsonX1+6.03*bankrupt$OhlsonX2-1.43*bankrupt$OhlsonX3
#  +0.0757*bankrupt$OhlsonX4-1.72*bankrupt$OhlsonX5-2.37*bankrupt$OhlsonX6
#-1.83*bankrupt$OhlsonX7+0.285*bankrupt$OhlsonX8-0.521*bankrupt$OhlsonX9

```


## Save Data

```{r}

bankrupt$Loss2years=NULL
bankrupt$EquityProxy=NULL
bankrupt$ROWMISS=NULL
bankrupt$Impute=NULL
bankrupt$NetDelta=NULL
write.csv(bankrupt, 'c:/users/lfult/documents/bankruptcy study/cleaned data.csv', row.names=F )

```

## Read Data

```{r}

bankrupt=read.csv('c:/users/lfult/documents/bankruptcy study/cleaned data.csv', stringsAsFactors = T)
bankrupt$Year=as.numeric(bankrupt$Year)

```


# Describe Data

```{r}


myprint(describe(bankrupt))

```

# Bankruptcies by State

```{r}

myshape=shapefile("cb_2018_us_state_500k.shp") 
myshape$M=as.numeric(myshape$STATEFP)
myf=function(x) mean(x)
formap=as.data.frame(aggregate(bankrupt$Bankrupt,by=list(bankrupt$GeoCode), FUN=myf))
colnames(formap)=c('M','Bankrupt')
formap=sp::merge(myshape,formap, by="M", all.x=F)
temp=formap
formap=NULL

```

## Map

```{r}


qpal<-colorBin(c("green", "orange", "red"), 0:2/10)
leaf=leaflet(temp) %>%
  addTiles(group = "OSM (default)") %>%
  addMapPane("borders", zIndex = 410) %>%
  #Base Diagrams
  addPolylines(data = temp,color = "black",
               opacity = 1, weight = 1, group="Borders", options = pathOptions(pane="borders"))%>%
  fitBounds(-124.8, -66.9, 24.4,49.4) %>% setView(-98.6, 39.83, zoom = 4)%>%
  addPolygons(stroke = FALSE,fillOpacity = 1, smoothFactor = 0.2, 
              color=~qpal(temp@data$Bankrupt), 
              popup = paste("State: ", temp@data$NAME, "<br>", 
                    "Bankruptices: ", temp@data$Bankrupt, "<br>"))%>%
  addLegend(data=temp, 
            "bottomright", opacity=1, pal = qpal, 
            values = ~temp@data$Bankrupt,
            title = "% Bankruptcies")

leaf

```


# Correlations

## Correlations among Income Statement and Balance Sheet

```{r}

myinc=bankrupt[,15:36]
corfunction(myinc)

```
## Correlations Among Medicare/Medicaid Variables

```{r}

mymed=bankrupt[,37:40]
corfunction(mymed)


```
## Correlation among Financial Ratios

```{r}

myrat=bankrupt[,41:51]
corfunction(myrat)

```




## Correlations Among Technical Variables

```{r}

mytech=bankrupt[,52:62]
corfunction(mytech)

```
## Correlations Among Quality Variables

```{r}

myq=bankrupt[,63:66]
corfunction(myq)

```
## Correlations Among Altman 

```{r}

myscores=bankrupt[,67:70]
corfunction(myscores)


```
## Correlations among Ohlson

```{r}

myscores=bankrupt[,71:78]
corfunction(myscores)


```


## Correlations among GLMData

```{r}

corfunction(glmdata)
glmdata$o1=NULL #perfectly correlated with a1

```


## Column Names

```{r}

colnames(bankrupt)


```
# Train Test Split

```{r}


  set.seed(1234)
  mys=sample(unique(bankrupt$HospID), 2237, replace=F)
  test=bankrupt[!bankrupt$HospID %in% mys,]
  train=bankrupt[bankrupt$HospID %in% mys,]
  length(unique(train$HospID[train$Bankrupt==1]))
  length(unique(test$HospID[test$Bankrupt==1]))
  train=train[,-c(1:11)]
  test=test[,-c(1:11)]
  



```


# Scale

Some methods are not scale invariant.

```{r}

for (i in 3:ncol(train)){
  ma=max(train[,i])
  mi=min(train[,i])
  train[,i]=(train[,i]-mi)/(ma-mi)
  test[,i]=(test[,i]-mi)/(ma-mi)
}

describe(train)

write.csv(train,'originaltrain.csv',row.names = F)
write.csv(test,'originaltest.csv', row.names=F)

```



# Oversample

We have highly imbalanced data. To improve classification we oversample the positive cases of bankruptcy using majority weighted oversampline. 

```{r}

tmp=mwmote(train, numInstances = 5000, classAttr="Bankrupt")
tmp$Bankrupt=round(tmp$Bankrupt,0)
train=rbind(train,tmp)
table(train$Bankrupt)
write.csv(train, 'oversampled.csv', row.names = F)
write.csv(test, 'testset.csv', row.names=F)
gc()

```
# Read

```{r}

train=read.csv('oversampled.csv', stringsAsFactors = T)
test=read.csv('testset.csv', stringsAsFactors = T)


```


# Confusion Matrix Function

This function is useful for some of the models. Others are done manually.

```{r}

mycm=function(model){
  tmp=round(predict(model,test, type='response'),0)
  tmp[tmp>1]=1
  return(confusionMatrix(as.factor(tmp), as.factor(test$Bankrupt), positive='1'))}

```


# Models

## Prep

```{r}



train1=train[,-2]
test1=test[,-2]
train2=train[,-1]
test2=test[, -2]


```

# Altman Ohlson

## Altman Only

```{r}

library(xgboost) #for fitting the xgboost model
library(randomForest)
library(caret)
library(party)

xgbtrain_x=data.matrix(train1[,-c(1:55,60:69)])
xgbtrain_y=train1[,1]

xgbtest_x=data.matrix(test1[,-c(1:55,60:69)])
xgbtest_y=test1[,1]

xgbtrain=xgb.DMatrix(xgbtrain_x,label=xgbtrain_y)

xgbtest=xgb.DMatrix(xgbtest_x,label=xgbtest_y)

watchlist = list(train=xgbtrain, test=xgbtest)
model = xgb.train(data = xgbtrain, max.depth = 3, watchlist=watchlist, nrounds = 70)

importance_matrix <- xgb.importance(colnames(train1[,56:59]), model =model)

mypred4=as.factor(round(predict(model,xgbtest),0))
confusionMatrix(table(mypred4,test1$Bankrupt), positive='1')

xgb.ggplot.importance(importance_matrix)


```

## Ohlson Only

```{r}

library(xgboost) #for fitting the xgboost model
library(randomForest)
library(caret)
library(party)

xgbtrain_x=data.matrix(train1[,-c(1:60, 69)])
xgbtrain_y=train1[,1]

xgbtest_x=data.matrix(test1[,-c(1:60, 69)])
xgbtest_y=test1[,1]

xgbtrain=xgb.DMatrix(xgbtrain_x,label=xgbtrain_y)

xgbtest=xgb.DMatrix(xgbtest_x,label=xgbtest_y)

watchlist = list(train=xgbtrain, test=xgbtest)
model = xgb.train(data = xgbtrain, max.depth = 3, watchlist=watchlist, nrounds = 70)

importance_matrix <- xgb.importance(colnames(train1[,61:68]), model =model)

mypred4=as.factor(round(predict(model,xgbtest),0))
confusionMatrix(table(mypred4,test1$Bankrupt), positive='1')

xgb.ggplot.importance(importance_matrix)


```

## XG Boost

```{r}


xgbtrain_x=data.matrix(train1[,-1])
xgbtrain_y=train1[,1]

xgbtest_x=data.matrix(test1[,-1])
xgbtest_y=test1[,1]

xgbtrain=xgb.DMatrix(xgbtrain_x,label=xgbtrain_y)

xgbtest=xgb.DMatrix(xgbtest_x,label=xgbtest_y)

watchlist = list(train=xgbtrain, test=xgbtest)
model = xgb.train(data = xgbtrain, max.depth = 150, watchlist=watchlist, nrounds = 70)

importance_matrix <- xgb.importance(colnames(train1[,-1]), model =model)

mypred4=as.factor(round(predict(model,xgbtest),0))
confusionMatrix(table(mypred4,test1$Bankrupt), positive='1')

xgb.ggplot.importance(importance_matrix, top_n=15)

```




#
